% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Šimon Kocúrek}
\address{Dúbravka 128, Košice \linebreak Slovakia 07215}
\contacts{+421 918 317 310 \linebreak simon.kocurek@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Full Stack Developer}{Lumeer.io}{Summer 2017 - present}
			\begin{itemize}
				\item Reduced time to render the user’s buddy list by 75\% by implementing prediction algorithm.
				\item Implemented iChat integration with OS X Spotlight Search by creating tool which extracts metadata from saved chat transcripts and provides metadata to a system-wide search database.
				\item Redesigned chat file format and implemented backwards compatibility for search.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Philadelphia, PA}{University of Pennsylvania}{Fall 2000 -- May 2005}
			\begin{itemize}
				\item M.S.E. in Computer and Information Science, May 2005. GPA: 3.6
				\item B.S.E. in Computer Science Engineering with Minor in Mathematics, May 2005.  In-major GPA: 3.4.
				\item Graduate Coursework: Software Foundations; Computer Architecture; Algorithms; Artificial Intelligence; Comparison of Learning Algorithms; Computational Theory.
				\item Undergraduate Coursework: Operating Systems; Databases; Algorithms; Programming Languages; Comp. Architecture; Engineering Entrepreneurship; Calculus III.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Multi-User Drawing Tool} (2004). Electronic classroom where multiple users can view and simultaneously draw on a “chalkboard” with each person’s edits synchronized.  C++, MFC
				\item \textbf{Synchronized Calendar} (2003 – 2004). Desktop calendar with globally shared and synchronized calendars, allowing users to schedule meetings with other users.  C\#.NET, SQL, XML
				\item \textbf{Operating System} (2002).  UNIX-style OS with scheduler, file system, text editor and calculator. C
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
				\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item C++; C; Java; Objective-C; C\#.NET; SQL; JavaScript; XSLT; XML (XSD) Schema 
				\item Visual Studio; Microsoft SQL Server; Eclipse; XCode; Interface Builder
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}

