\documentclass[]{style}

\usepackage{amsmath}

\name{Šimon Kocúrek}
\address{Dúbravka 128, 072 15\linebreak Slovakia}
\contacts{+421 918 317 310\linebreak simon.kocurek@gmail.com}

\begin{document}

	\makeheader

	\begin{cvsection}{Employment}
	
    	\begin{cvsubsection}{C\# Developer}{Siemens Healthineers}{Nov 2019 — Present}
			\begin{itemize}
			    \item Working on remote control and monitoring capabilities for medical devices.
			    \item Was a lead developer on scalable secure tunneling between medical devices and AWS backend.
			    \item Mentored a junior developer, helping him complete tasks and grow his technical skills.
			    \item \textbf{Technologies:} .Net Framework, ASP.Net Core, Docker, Typescript, Git
			\end{itemize}
		\end{cvsubsection}
		
    	\begin{cvsubsection}{Java Developer Part-time}{IBM}{Jan 2019 — Nov 2019}
			\begin{itemize}
    			\item Worked on IoT solution for controlling indoor lights using a distributed network of controllers.
    			\item Introduced static analysis on the frontend.
    			\item \textbf{Technologies:} Java, Gradle, Javascript, Bash, SQL, Git
			\end{itemize}
		\end{cvsubsection}
		
    	\begin{cvsubsection}{DevOps Intern}{IBM}{Sep 2018 — Dec 2018}
			\begin{itemize}
			    \item Wrote scripts simulating production Kubernetes cluster locally using Minikube.
			    \item Made testing microservices possible on developer machines.
			    \item \textbf{Technologies:} Kubernetes, Docker, Minikube, Bash, Jenkins, Helm, Spring Boot
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Developer Part-time}{Lumeer.io}{Jul 2017 — May 2018}
			\begin{itemize}
			    \item Worked on both backend and frontend of web application for management of local businesses.
				\item \textbf{Technologies:} Angular, Typescript, Java, JBoss, Maven, MongoDb
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Košice}{Pavol Jozef Šafárik Uni}{Sep 2016 — Jun 2019}
			\begin{itemize}
				\item Bachelor's degree in Applied Computer Science. GPA: 4.73 (out of 5)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Free Time}
	    \begin{cvsubsection}{Personal Projects}{}{github.com/SimonKocurek}
			\begin{itemize}
			    \item Worked on IoT project for personalized digital signage - zirro.ics.upjs.sk
			    \item Created and published an Android application - github.com/SimonKocurek/Trebis
			    \item Coded maze generation game - github.com/SimonKocurek/Mazes
			    \item Made simple IoT snake game - gist.github.com/SimonKocurek/85ff49d41208fbdccd65d3dac5968b42
			\end{itemize}
		\end{cvsubsection}

	\end{cvsection}
	
	\begin{cvsection}{Spoken Languages}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
                \item \textbf{English:} Full professional proficiency.
                \item \textbf{German:} Limited working proficiency.
                \item \textbf{Slovak:} Native proficiency.
                \item \textbf{Czech:} Full professional proficiency.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Soft Skills}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
                \item Experienced with working on Agile projects spanning across multiple teams from different countries.
                \item Attending local hackatons, conferences and lectures.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	
\end{document}
